A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Fixing tables and figures

\begin{lstlisting}
> eval(2)
[1] 2
> eval(expression(1+2))
[1] 3
> eval(parse(text = "1 + 2"))
[1] 3
\end{lstlisting}

@@

We compare the number of events intercepted during execution of \eval across the
whole corpus. For this, we use the number of interpreter's evaluator loops as a
proxy for events. In the corpus, we observe \AllEventCountRnd events. Only
\EvalEventCountRnd events occur inside eval. This is just \EvalEventAllPerc of
all events. Figure~\ref{fig:event-distribution} shows the distribution of events
caused by \eval calls from R Core and CRAN packages.

@@

We further investigate the type of input passed to \eval in
Figure~\cite{fig:eval-expression-kind} by the type of input and
the source of \eval. In this figure, \emph{Expression} is the type of program text,
\emph{Environmment} is the type of scopes or environments used for binding,
\emph{Null} is the type of the unique \c{NULL} object, \emph{Vector} is the type
assigned to vectors of strings, booleans, integers, reals and bytes;
\emph{Symbol} is the type of unevaluated symbols, and \emph{Function} is the
type of functions.

>>>>

%\begin{lstlisting}
%> eval(2)
%[1] 2
%> eval(expression(1+2))
%[1] 3
%> eval(parse(text = "1 + 2"))
%[1] 3
%\end{lstlisting}

@@

We compare the number of events intercepted during execution of \eval across the
whole corpus. For this, we use the number of interpreter's evaluator loops as a
proxy for events. In the corpus, we observe \AllEventCountRnd events. Only
\EvalEventCountRnd events occur inside eval. This is just \EvalEventAllPerc of
all events. Table~\ref{table:event-distribution} shows the distribution of events
caused by \eval calls from R Core and CRAN packages.

@@

We further investigate the type of input passed to \eval in
Figure~\ref{fig:eval-expression-kind} by the type of input and
the source of \eval. In this figure, \emph{Expression} is the type of program text,
\emph{Environmment} is the type of scopes or environments used for binding,
\emph{Null} is the type of the unique \c{NULL} object, \emph{Vector} is the type
assigned to vectors of strings, booleans, integers, reals and bytes;
\emph{Symbol} is the type of unevaluated symbols, and \emph{Function} is the
type of functions.
